FoRTE baseline

### 2019-03-27 analysis/paper/paper.Rmd
Add old LAI parameter uncertainty analysis to paper

@@

### Additional references

@katul_2003_relationship

@@

## General outline

@@

The Ecosystem Demography Model, version 2 (ED2) [@medvigy_2009_mechanistic].

@@

- Cohort-based scaling approach
- Photosynthesis / stomatal conductance
- Allometries

@@

@@

```{r captions, include = FALSE}
lai_10yr_cap <- paste(
  "ED2 leaf area index (LAI) predictions by plant functional type."
)

rad_barplot_cap <- paste(
  "Comparison of radiation profiles under two-stream and multiple scatter",
  "canopy radiative transfer models."
)
```

@@

@@

>>>>

        - FoRTE project -- Forecasting a disturbance.
            - Compare ecological resilience/memory between model and reality

Journal ideas:

- _Global Change Biology_ -- 8000 word limit may be OK, especially if many methodological details are punted to the appendices.
- _Ecological Monographs_ -- To do this topic justice may require a lot of words and figures. It may be hard to squeeze all of this information into a regular research paper.

@@

@@

@@

The Ecosystem Demography Model, version 2.X (ED2) [@medvigy_2009_mechanistic].

@@

- Cohort-based scaling approach
- Photosynthesis / stomatal conductance
    - I think I need to cite @katul_2003_relationship somewhere in here
- Allometries

@@

## Data sources

TRY data [@kattge_2011_try].

Other data from FoRTE? FIA? Remote sensing?

## Modeling workflow

PEcAn parameter sensitivity and uncertainty analysis [@lebauer_2013_facilitating].
Other PEcAn references: [@dietze_2013_improving].

{TODO: Conceptual diagram of workflow}

@@

```{r captions}
lai_10yr_cap <- paste(
  "ED2 leaf area index (LAI) predictions by plant functional type."
)

rad_barplot_cap <- paste(
  "Comparison of radiation profiles under two-stream and multiple scatter",
  "canopy radiative transfer models."
)

annual_lai_workflows_cap <- paste(
  "Max annual leaf area index predictions by plant functional type",
  "across different parameter combinations."
)
```

@@

## Structural uncertainty

@@

Compared to the default two-stream model, the multiple scatter model leads to slightly less beam (direct) radiation in the understory but slightly more diffuse radiation.

## Parameter uncertainty

{TODO: PEcAn variance decomposition analysis, by configuration.}

```{r annual_lai_workflows, fig.cap = annual_lai_workflows_cap, fig.dim = c(10, 8)}
readd(old_lai_plot)
```

`r mdcap(annual_lai_workflows_cap)`

Different parameter combinations produce
